\documentclass{article}
\usepackage{helvet}
\usepackage{hyperref}
\usepackage{xstring}
\renewcommand{\familydefault}{\sfdefault}
\newcommand{\printvalues}{topsep=\the\topsep; itemsep=\the\itemsep; parsep=\the\parsep; partopsep=\the\partopsep}
%\newcommand{\jobRole}{staff} % This will be dynamically set by the script

%
\pagestyle{empty}        % no page numbers, thanks.
\addtolength{\topmargin}{-1.2in}% repairing LaTeX's huge margins...
\addtolength{\leftmargin}{2.4in}  % same here....
\setlength{\oddsidemargin}{0.5in}
\addtolength{\textwidth}{1.3in} % and here...
\addtolength{\marginparsep}{0in}
\setlength{\parindent}{0mm}  % indented paragraphs just don't make it
                    % on a resume.  (My opinion; if you
                    % disagree, give this whatever value you
                    % want.) 
\setlength{\textheight}{10in}  % more margin hacking.  I have a large
                    % resume to fit on one page.
\StrSubstitute{\jobRole}{-}{ }[\jobRoleFormatted]
\begin{document}
\fontsize{9pt}{10.5pt}\selectfont

\begin{center}
\large{\bf Adriano Vieira Petrich}    % make the name stand out
\end{center}
\reversemarginpar        % this puts the margin notes on the left-hand side of the resume.
\par
petrich@gmail.com \hspace*{\fill} Phone (+49) 01575 1453514
\par
Berlin, DE \hspace*{\fill}

\par
%\vspace{2\baselineskip}
\vspace{\baselineskip}
%\par
%\vspace{\baselineskip}
%\marginpar{\rule{7.2in}{0.4mm}}
\vspace{.1in}

\par
\jobRoleFormatted  Engineer from Brazil with Permanent Residency living in Berlin with 20 years of experience \marginpar{{\bf About me}}
in designing and architecting cutting-edge distributed systems and backend solutions.
Renowned for advanced Python expertise, having made significant contributions to OpenStack at Red Hat, where I led the development of core components and engineered a highly efficient workflow engine.
Highly skilled in building scalable, secure APIs, designing robust cloud infrastructure, and delivering top-tier secure applications.
Known for combining deep technical proficiency with the ability to simplify complex problems, mentor high-performing teams, and deliver innovative, high-impact software solutions across diverse industries and environments.



\vspace{\baselineskip}
\par

\par
Programming Languages \& Core Technologies: Python, Rust, Java, Async(Celery, Kafka, fastAPI) \marginpar{{\bf Technical\par Expertise}}
\par
Cloud \& Infrastructure: Ansible, OpenStack, Containerization, Virtualization, Docker, prometheus 
\par
Architecture \& Design: Distributed Systems, Microservices, Security Gateways, L4 Microkernel
\par
Data \& Machine Learning: SQL/NoSQL, Machine Learning, NLP, Computer Vision, GIS 
\par
Development Practices: Test-Driven Development (TDD), Behavior-Driven Development (BDD), Continuous Integration/Continuous Deployment (CI/CD), Agile/SCRUM  
\par
Operating Systems \& Tools: Linux (Advanced), System Automation 
\par
Languages: English (Fluent), Portuguese (Native), Basic French, Basic Spanish
\vspace{\baselineskip}

\vspace{.03in}
\par
\vspace{\baselineskip}
\marginpar{\rule{7.2in}{0.4mm}}
\vspace{.1in}
{\bf Senior Developer at Infodas GmbH} \marginpar{{\bf Experience}}
\hfill {{\bf 2022 --- 2025 }}
\par
\vspace{.01in}
Development of a embedded content-aware gateway for industrial applications, integrating Rust, Python, and Ansible. Responsible for integration from baremetal kernel, virtualizations, and user level applications.
\begin{itemize}
\setlength{\topsep}{0mm}
\setlength{\itemsep}{0mm}
\setlength{\parsep}{0mm}
%    \item\printvalues
    \item Rust \& Embedded Systems: Developed a content-aware gateway using Rust on an L4 microkernel, ensuring memory safety, real-time performance, and secure execution in industrial environments.
    \item Systems Integration \& Automation: Engineered seamless integration between Rust modules, Python automation, and Ansible-based infrastructure, optimizing embedded system interactions and deployment processes. 
    \item Performance, Security \& Collaboration: Optimized low-level system performance, enforced secure coding practices, and acted as the key integration point between Systems and Platform teams for scalable, maintainable solutions.
\end{itemize}
\par
%\vspace{\baselineskip}


{\bf Software Engineer at Red Hat (limited UK then GmbH)}: Major enterprise open-source software company, serving 90\% of Fortune 500 companies.
\hfill {{\bf 2015 --- 2022 }}
\par
\vspace{.01in}
Developed and maintained OpenStack (TripleO), optimizing scalability and reliability.
Served as the primary contact for Bugzilla, streamlining issue resolution.
Specialized in automation with Python and Ansible for efficient deployment and management.
\begin{itemize}
\setlength{\itemsep}{0mm}
\setlength{\parsep}{0mm}
    \item OpenStack Development \& Maintenance: Led initial development and ongoing maintenance of OpenStack (TripleO) with a focus on automation using Python and Ansible. 
    \item CI/CD \& Workflow Orchestration: Engineered CI pipelines with Jenkins and Zuul; contributed as Core and DTL to Mistral, an open-source workflow engine.
    \item Scalable Cloud Infrastructure: Worked with large codebases, leveraging Python, Ansible, Bash, containers, and virtualization for orchestration in enterprise environments.
\end{itemize}
\par
%\vspace{\baselineskip}

{\bf Senior Developer at Hogarth Worldwide}: One of the world's largest marketing production agencies, part of WPP Group)
\hfill {{\bf 2013 --- 2015 }}
\par
\vspace{.01in}
Maintained and enhanced a CRM for advertisement management, optimizing workflows across all aspects of digital media creation.
Worked extensively with Python to handle large-scale data processing, leveraging S3 for efficient storage and retrieval of large media files.
\begin{itemize}
\setlength{\itemsep}{0mm}
\setlength{\parsep}{0mm}
    \item Cloud-Based Asset Management: Developed a provider-agnostic system using Django for scalable and flexible cloud deployment. 
    \item Agile Development: Built using SCRUM, emphasizing iterative improvements and collaboration.
    \item Quality \& Automation: Applied TDD, BDD, and CI to ensure reliability, test coverage, and seamless integration.
\end{itemize}
\par
%\vspace{\baselineskip}

{\bf Lead Developer and Tech Lead at VirtualX Brasil}
\hfill {{\bf 2011 --- 2013 }}
\par
\vspace{.01in}
\begin{itemize}
\setlength{\itemsep}{0mm}
\setlength{\parsep}{0mm}
    \item Startup Innovation: Contributed to a startup focused on delivering semantic knowledge for online products in Brazil, driving product intelligence and insights. 
    \item Advanced Technologies: Utilized Machine Learning, Natural Language Processing (NLP), Computer Vision, and NoSQL to build scalable, intelligent systems.
    \item Team Leadership \& Collaboration: Coordinated and acted as the liaison between the development team and Virginia Tech partnership while managing a local team for seamless project execution.
\end{itemize}
\par
%\vspace{\baselineskip}

{\bf Various Software Development Jobs}    
\hfill {{\bf 2000 --- 2013 }}
\par
\vspace{.03in}
With extensive experience across diverse industries including environmental monitoring, NGO support, banking, healthcare, telecommunications, and internet services, 
I have successfully led and contributed to the development of innovative solutions using cutting-edge technologies.
\begin{itemize}
\setlength{\leftmargin}{1.4in}
\setlength{\itemsep}{0mm}
\setlength{\parsep}{0mm}

    \item {\bf Deforestation Monitoring } Developed a Django-GIS app for satellite imagery analysis to combat Amazon deforestation, mentoring a team for long-term maintenance. 
    \item {\bf NGO Application Development } Led development, training, and mentoring efforts for a Django-based application supporting an NGO with unique scalability requirements.

    \item {\bf Banking Solutions } Served as Tech Lead for a large Java team, delivering a robust offline banking solution for a major financial institution. 

    \item {\bf Healthcare Technology } Founded and led a startup, creating full-stack web and mobile applications focused on diabetes management. 

    \item {\bf Remote Desktop Technology} Oversaw offshore team development of a Linux-based remote window service server, utilizing Nomachine for efficient remote access. 

    \item {\bf ISP Infrastructure} Designed and integrated an ISP system, implementing JBoss, MySQL, RADIUS, and POTS for robust core infrastructure.

\end{itemize} 
\vspace{\baselineskip}
\marginpar{\rule{7.2in}{0.4mm}}
\vspace{.1in}
I don't have a bachelor's degree, having left university to focus on programming.  
However, as I have since accumulated significant work experience, and as I am an avid self-taught learner, I don't think this limits my abilities as a developer.
\par

%\vspace{\baselineskip}

{\bf Physics Bachelor - Instituto de F\'{\i}sica USP} \hspace*{\fill} {{\bf 1995 --- 2003 }} \marginpar{{\bf Education}}
\par
\vspace{.03in}

Specialized in the practical applications of physics, with a focus on developing innovative instrumentation,
data acquisition systems, and analog-to-digital conversion.
Gained hands-on experience in designing and implementing complex systems for scientific research.
Completed additional coursework in biology and hardware design, expanding interdisciplinary knowledge and enhancing the
ability to bridge the gap between software and hardware in real-world applications. This foundational experience has
honed my problem-solving skills and deepened my technical versatility, which I continue to leverage in software engineering.
\par

\vspace{\baselineskip}
{\bf Electrical Engineering - Escola de Engenharia Mackenzie} \hspace*{\fill} {{\bf 1992 --- 1995 }}
\par
\vspace{.03in}
Programming: C and Pascal, developing foundational skills in software development and algorithm design. 
\par
Mathematics: Linear Algebra and Numerical Calculus, providing a solid understanding of mathematical modeling, problem-solving, and computational methods.
\par
\vspace{\baselineskip}
\marginpar{\rule{7.2in}{0.4mm}}
\vspace{.1in}


{\bf Mistral - Project Update } \marginpar{{\bf Presentations and Courses }} 
\vspace{.03in}
\par
Openstack Summit Berlin 2018 
\par
\vspace{\baselineskip}
{\bf Yak shaving a good place to eat using non negative matrix factorization }
\vspace{.03in}
\par
Using data analysis to find a place to eat.
\par
Europython 2015. Slides: http://slidesha.re/nbTsaP
\par
\vspace{\baselineskip}
{\bf Procrastinating with Celery } (presented in Portuguese)
\par
TDC 2011 (The Developers Conference 2011). Slides: http://slidesha.re/nbTsaP
\par
\vspace{\baselineskip}
{\bf Test Driven Development in Django, no excuses } (presented in Portuguese)  
\par
FISL 11 (11th International Free Software Forum) in 2010 and in TDC 2010 (The Developers Conference 2010). Slides: http://slidesha.re/b9xHYp
\par
\vspace{\baselineskip}
{\bf Starting with TDD and BDD in Django } (presented in Portuguese)
\par
PythonBrasil[6] in 2010.
\vspace{\baselineskip}
\par
{\bf From 0 to Python to Django } (presented in Portuguese)
\par
A 80 hour course that starts with the basic principles of python and OO and ends with advanced django.
Taught at both Globo.com and Globosat, members of the largest media company in Brazil.
\vspace{.03in}
\par
\vspace{\baselineskip}
\marginpar{\rule{7.2in}{0.4mm}}
\vspace{.1in}


{\bf ADK challenge for Google Developer Day 2011 }
\marginpar{{\bf Awards and Contests}}
\vspace{.03in}
\par
One of the ten Brazilian finalists for the Android Development Kit challenge. 
\par
\href{https://sites.google.com/site/opencallforgdd/the-challenge}{https://sites.google.com/site/opencallforgdd/the-challenge}

\par
\vspace{\baselineskip}

%\marginpar{\rule{7.2in}{0.4mm}}
%\vspace{.1in}


%{\bf Other Links and Interests}
%\marginpar{{\bf Other Links and Interests}}
%\par
%github \href{http://github.com/frac}{http://github.com/frac}  slideshare \href{http://www.slideshare.net/fractalk}{http://www.slideshare.net/fractalk}
%\par
%I was founder and organiser of the \href{http://twitter.com/pythondundee}{python dundee} user group.
%\par
%%\begin{center}\small This document is done in \LaTeX\end{center}
\end{document}

